Title Placeholder

### 2012-08-05 text/ptf_microlensing_paper.tex
worked on paper

\section{Introduction}

\section{PTF Observations and Data}

\section{Simulated microlensing event recovery}

\section{Searching for events in full PTF data set}

@@

\section{Conclusions and Future Work}

>>>>

\section{Introduction}
Since Einstein first studied gravitational microlensing (cite), the phenomena has been used to study dark objects, probe galactic structure and kinematics, and discover extrasolar planets. Microlensing events were once relatively rare, but with advances in CCD technology and the help of several dedicated microlensing surveys (), $>500$ lensing events are now detected per observing season.

[MORE MICROLENSING INTRODUCTION]

[QUICK INTRO TO THEORY AND JARGON]

[MOTIVATION FOR PROJECT -- Han, Di Stefano, Di Stefano et al. -- mesolensing and near-field microlensing]

\section{PTF Observations and Data}
[TODO: Marcel]

\section{Microlensing event recovery}
Microlensing surveys typically use difference image analysis (cite Lupton?) to initially identify transient events and then analyze the candidate light curves to search for microlensing events (cite MACHO, OGLE). This method is essential for studying crowded fields such as the Galactic bulge, and also limits the number of light curves that must be searched for microlensing events, thus saving on computation time. This [method] also provides real-time detection of events so surveys can utilize networks of telescopes to provide follow-up observations of these transients. Our approach is to instead take the preexisting PTF light curve database over the entire survey footprint and develop fast, robust search algorithms to pick out microlensing event candidates from this massive data archive.

In order to develop predictions for event rates and then eventually use observed event rates to infer [] we must understand our microlensing event recovery rate, or \textit{detection efficiency}, $\varepsilon$. The detection efficiency is commonly expressed as a function of microlensing event timescale and is therefore a function of survey parameters, such as cadence and baseline [FIGURE simulated detection efficiency]. [What did MACHO do exactly? What does OGLE do?] The nature of the PTF survey means that different fields are observed with very different sampling patterns [FIGURE showing different sampling]. We must compute the detection efficiency for each field individually.

We compute the detection efficiency with a Monte Carlo simulation over real data. For a particular field of interest, we randomly sample 11,000 light curves from the database with $>25$ ``good'' observations. [define ``good'']. We compute a set of variability statistics for each light curve, we then iterate and add 100 different simulated microlensing events to each light curve and recompute the variability statistics after each iteration [Figures here?]. The parameters for the random microlensing events are chosen as follows: 
\begin{align}
	t_0&\sim\mathcal{U}[t_{min}, t_{max}] \\
	u_0&\sim\mathcal{U}[0, 1] \\
	\log_{10}t_E&\sim\mathcal{U}[0, 3] 
\end{align}
where $\mathcal{U}$ is a uniform distribution.

[How to compute detection efficiency?] [Specifics of our method, e.g. details about my code]

[Parts of the above text will get absorbed into sections below]

\subsection{Selecting candidate microlensing events}
- Proper statistical modeling is too time consuming, so we first have to define some selection criteria to limit the sample (number of good observations, quality cuts, etc.)

- Discuss $\Delta \chi^2$ method, downfalls (speed, not robust -- how do you define the threshold?)

- Shin et al. paper

- Introduce variability statistics: define them, what they pick out, what they have been used for before

\subsection{Detection efficiency}
- Previous surveys had fairly uniform time sampling, and smaller areas

- With PTF, fields have vastly different sampling patterns, baselines, and cadences

- We have to consider the efficiency on a field-by-field basis

- Show detection efficiency of each variability statistic

\section{Searching for events in full PTF data set}
- Describe pipeline for events ... ?

@@

\section{Conclusions and Future Work}
\subsection{Globular Clusters and Other Overdensities}
- Do they contribute to the lensing rate?
